---
title: "Drill Pasture Organized"
author: "Maria Stahl"
date: "10/26/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
rm(list = ls())
```

## Load necessary packages
```{r}
library(amt)
library(dplyr)
library(ggplot2)
library(glmnetUtils)
library(hms)
library(lubridate)
library(raster)
library(rgdal)
library(rlist)
library(sf)
library(stats)
library(tidyr)
library(tmap)
```

## Load in Drill Pasture shapefile
```{r}
drill_pasture = readOGR("Drill_Pasture/Drill_Pasture.shp")
drill_pasture_sf = st_read("Drill_Pasture/Drill_Pasture.shp")
```

## Load in RAP data (raster created through Google Earth Engine)
```{r}
veg.dat.2020.small = stack('RAP_VegCover_2020_new.tif')

veg.dat.2020.new = stack('RAP3_2020.tif')

# reproject RAP data to UTM
veg.dat.2020.small =
  projectRaster(veg.dat.2020.small, crs = crs(drill_pasture))
veg.dat.2020.small$herb = sum(veg.dat.2020.small$AFGC,
                              veg.dat.2020.small$PFGC)
veg.dat.2020.new =
  projectRaster(veg.dat.2020.new, crs = crs(drill_pasture))
veg.dat.2020.new$herb = sum(veg.dat.2020.new$AFG,
                              veg.dat.2020.new$PFG)

# mask full raster stack to cover only Drill Pasture
DPveg = mask(veg.dat.2020.new, drill_pasture)
DPveg.new = mask(veg.dat.2020.new, drill_pasture)

par(mfrow = c(1,2))
plot(DPveg.new$SHR)
plot(DPveg$SHR)
```

## remove areas with >25% herbaceous cover
We do this to remove the shadow from the mesa walls
```{r}
herb.buffered = DPveg$herb
herb.buffered[herb.buffered > 25] = NA
```

## Read in elevation data and calculate ruggedness and slope (elev data from https://www.sciencebase.gov/catalog/item/5f7784be82ce1d74e7d6ca12)
```{r}
elev_orig = raster('USGS_13_n39w110.tif')
temp = raster(extent(drill_pasture@bbox), crs = crs(drill_pasture),
              resolution = 10)
elev2 = projectRaster(elev_orig, temp)
names(elev2) = 'drill_elev'

# calculate ruggedness and slope
ruggedness = terrain(elev2, opt = 'TRI', neighbors = 8)
slope = terrain(elev2, opt = 'slope', neighbors = 8)
```

<!-- ## Read in soil classification data and state transition data (soil data from -->
<!-- https://www.sciencebase.gov/catalog/item/5f76119e82cef8d1839c681d) -->
<!-- ```{r} -->
<!-- soilClasses = raster('SGU_1st_Class/SGU_1st_Class.tif') -->
<!-- soilClasses2 = projectRaster(soilClasses, temp) -->

<!-- stateTransition = stack('Grassland_StateTransition_Map_CANY_IndianCreek/Grassland_StateTransition_Map_CANY_IndianCreek.tif') -->
<!-- stateTransition2 = projectRaster(stateTransition, temp) -->
<!-- ``` -->

## Load in collar data
```{r}
cattle.dat.new = read.csv('GPS Combined 2020-21 Winter.csv')
cattle.dat.new = distinct(cattle.dat.new)

# check how many individuals are in dataset
levels(as.factor(cattle.dat.new$COLLAR))

# data in UTM
cattle.gps.new = st_as_sf(cattle.dat.new, coords = c('LONGITUDE', 'LATITUDE'))
st_crs(cattle.gps.new) = CRS("+proj=longlat +ellps=WGS84")
cattle.gps.new$geometry = st_transform(cattle.gps.new$geometry, 
                         crs = st_crs(drill_pasture))

projection(cattle.gps.new) == projection(drill_pasture)

cattle.utm.new = as_Spatial(cattle.gps.new)

# remove data points outside of Drill Pasture
test = cattle.utm.new[!is.na(over(cattle.utm.new, as(drill_pasture,
                                                 'SpatialPolygons'))),]

# remove data points outside of buffered herb area
selection = !is.na(over(cattle.utm.new, rasterToPolygons(herb.buffered)))
DPcattle.dat.new = cattle.utm.new[array(selection),]

tm_shape(herb.buffered) + tm_raster() +
  tm_shape(test) + tm_dots() +
  tm_shape(drill_pasture) + tm_borders()

rm(cattle.gps.new)
```

## CLEAN UP DPcattle.dat
```{r}
DPcattle.dat.new$date_time =
  as.POSIXct(DPcattle.dat.new@data[['GMT_TIME']],
           format = '%Y-%m-%d %H:%M:%S', tz = 'GMT')
DPcattle.dat.new$date_time =
  with_tz(DPcattle.dat.new@data[['date_time']], tz = 'US/Mountain')
```

## Calculate distance from water and salt licks
```{r}
# read in KMZ file and convert to UTM
features = read_sf('Drill 2020 water and salt.kml')
features$Name = c('trough1', 'trough2', 'trough3', 'trough4', 'trough5',
                  'salt_lick1', 'salt1', 'salt2', 'salt3', 'salt_lick4', 
                  'creek_trough')
features$Description = c('water', 'water', 'water', 'water', 'water', 'salt',
                         'salt', 'salt', 'salt', 'salt', 'outside')
features$geometry = st_transform(features$geometry, crs = crs(drill_pasture_sf))

indianCreek = read_sf('indian creek.kml') %>%
  st_transform(crs = crs(drill_pasture)) %>%
  st_cast(to = 'POINT')
indianCreek$Description = rep('water', times = dim(indianCreek)[1])

featuresAll = rbind(features, indianCreek)

# create distance raster
water = distanceFromPoints(herb.buffered,
                           st_coordinates(filter(featuresAll, 
                                                 Description == 'water'))[ ,1:2])
names(water) = 'close_water'
salt = distanceFromPoints(herb.buffered,
                           st_coordinates(filter(featuresAll, 
                                                 Description == 'salt'))[ ,1:2])
names(salt) = 'close_salt'

log.water = log(water)
names(log.water) = 'log_water'
log.salt = log(salt)
names(log.salt) = 'log_salt'
```

## Resample and scale all covariates

### THIS SHOULD BE REVISITED, PER BRIAN'S COMMENTS
```{r}
elev.small = resample(elev2, herb.buffered, method = 'ngb') %>%
  mask(herb.buffered)
slope.small = resample(slope, herb.buffered$herb, method = 'ngb') %>%
  mask(herb.buffered)
ruggedness.small = resample(ruggedness, herb.buffered, method = 'ngb') %>%
  mask(herb.buffered)
water.small = resample(log.water, herb.buffered, method = 'ngb') %>%
  mask(herb.buffered)
salt.small = resample(log.salt, herb.buffered, method = 'ngb') %>%
  mask(herb.buffered)
SHR.small = mask(DPveg$SHR, herb.buffered)
TREE.small = mask(DPveg$TRE, herb.buffered)

scaled.elev = scale(elev.small, center = T)
scaled.slope = scale(slope.small, center = T)
scaled.ruggedness = scale(ruggedness.small, center = T)
names(scaled.elev) = 'drill_elev'
names(scaled.slope) = 'slope'
scaled.water = scale(water.small, center = T)
scaled.salt = scale(salt.small, center = T)
names(scaled.water) = 'log_water'
names(scaled.salt) = 'log_salt'
scaled.herb = scale(herb.buffered, center = T)
scaled.SHR = scale(SHR.small, center = T)
scaled.TREE = scale(TREE.small, center = T)

# scaled.soil = resample(soilClasses2, herb.buffered, method = 'ngb') %>%
#   scale(center = T)
# names(scaled.soil) = 'soil_class'
```

## Load in Roads shapefile
```{r}
roads = readOGR("roads San Juan County/roads_49037_2014.shp")
roads = spTransform(roads, crs(crs(drill_pasture)))
roads = st_crop(st_as_sf(roads), drill_pasture)
```

## Calculate activity modes
```{r}
# create track for individuals
DPcattle.frame = as.data.frame(DPcattle.dat.new)
DPcattle.frame = DPcattle.frame[!is.na(DPcattle.frame$date_time),]
DPcattle.frame$COLLAR = as.factor(DPcattle.frame$COLLAR)
DPcattle.list = split(DPcattle.frame, f = DPcattle.frame$COLLAR)
DPtrack = lapply(DPcattle.list, FUN = mk_track, .x = coords.x1, .y = coords.x2,
                 .t = date_time, crs = crs(DPcattle.dat.new), order_by_ts = T,
                 check_duplicates = T)
DPtrack = DPtrack[-8]
rm(DPcattle.list)

breeds = distinct(DPcattle.frame[3:4])[order(distinct(DPcattle.frame[4])),]

# calculate velocity from track
collars = levels(as.factor(DPcattle.dat.new$COLLAR))[-8]
DPspeed = lapply(DPtrack, FUN = speed)
for(i in seq(1:length(collars))){
  c = collars[i]
  DPtrack[[c]][4] = DPspeed[[c]]
  names(DPtrack[[c]])[4] = 'speed'
}

# convert list back into data.frame
DPspeed.frame = list.rbind(DPtrack)
temp = array()
for(i in seq(1:length(collars))){
  temp = append(temp, rep(collars[i], times = dim(DPtrack[[i]])[1]))
}
temp = temp[!is.na(temp)]
DPspeed.frame$COLLAR = temp
names(DPspeed.frame)[3] = 'date_time'
rm(DPtrack)

# merge DPcattle.frame and DPspeed.frame
DPcattle.frame = merge(DPcattle.frame, DPspeed.frame, 
                       by = c('COLLAR','date_time'))[-c(15,16),]

# classify activity based on speed (from Nyamuryekung'e et al. 2021a)
resting = 2.34/60 # max resting speed in m/s
grazing = 25/60 # max grazing speed in m/s
DPcattle.frame$activity = array()
DPcattle.frame$activity[DPcattle.frame$speed <= resting] = 'resting'
DPcattle.frame$activity[DPcattle.frame$speed > resting &
                          DPcattle.frame$speed <= grazing] = 'grazing'
DPcattle.frame$activity[DPcattle.frame$speed > grazing] = 'traveling'
DPcattle.frame$time = as_hms(DPcattle.frame$date_time)

DPcattle.track = mk_track(DPcattle.frame, .x = coords.x1, .y = coords.x2, 
                          .t = date_time, COLLAR = COLLAR, BREED = BREED, 
                          ALTITUDE = ALTITUDE,
                          TEMPERATURE = TEMPERATURE, DOP = DOP,
                          SATELLITES = SATELLITES, speed = speed, 
                          activity = activity, time = time, date = date_time)

```

## Prepare all data for model selection
```{r}
# create grid of available points
# avail.border = st_difference(drill_pasture_sf, buffer) %>%
#   as_Spatial()
avail = as.data.frame(herb.buffered, xy = T)
avail$case_ = rep(0, dim(avail)[1])
avail = avail[,-3]
names(avail) = c('x_', 'y_', 'case_')
avail.small = avail[seq(1,dim(avail)[1],100),] # select every 100th pt

# remove points from first and last three days
entry = sort(DPcattle.track$date, na.rm = T)[7]
exit = max(DPcattle.track$date, na.rm = T)
DPcattle.track.cropped = DPcattle.track %>%
  filter(date > (entry + 3) & date < (exit - 3))
DPcattle.frame.cropped = as.data.frame(DPcattle.track.cropped)

# create separate datasets for each activity level for each invididual
all.list = split(x = DPcattle.track.cropped, 
                 f = as.factor(DPcattle.track.cropped$COLLAR))[-8]
all.list = lapply(all.list, `[`, c(1,2))
```

## LASSO MODEL SELECTION
No TREE or tri or soil
```{r}
set.seed(seed = 1)

HSFmodel = function(used, avail) {
  used$case_ = 1
  avail$case_ = 0
  all.points = rbind(used, avail)
  all.points = all.points  %>%
    #attach env covariates to observed and available pts
    extract_covariates(scaled.elev) %>%
    extract_covariates(scaled.slope) %>%
    extract_covariates(scaled.water) %>%
    extract_covariates(scaled.salt) %>%
    extract_covariates(scaled.herb) %>%
    extract_covariates(scaled.SHR) %>%
    mutate(w = ifelse(case_, 1, 1e3))
  model = glmnetUtils::cv.glmnet(case_ ~ drill_elev + slope +
                                   log_water + log_salt + herb + SHR,
              data = all.points, weights = w,
                   family = binomial(link = 'logit'))
  return(model)
}

all.model.list8 = lapply(X = all.list, FUN = HSFmodel, avail = avail)

indivBreed = c("80333 - Angus", "80335 - Angus", "80338 - Criollo",
               "80339 - Angus", "80342 - Criollo", "80343 - Angus",
               "80344 - Criollo", "80349 - Criollo", "80351 - Criollo")

cf.all = cbind(
  as.array(coef(all.model.list8[[1]])), as.array(coef(all.model.list8[[2]])),
  as.array(coef(all.model.list8[[3]])), as.array(coef(all.model.list8[[4]])),
  as.array(coef(all.model.list8[[5]])), as.array(coef(all.model.list8[[6]])),
  as.array(coef(all.model.list8[[7]])), as.array(coef(all.model.list8[[8]])),
  as.array(coef(all.model.list8[[9]])))
colnames(cf.all) = indivBreed
write.csv(cf.all, 'coefficientsAll.LASSO - with RAP and soil.csv')

```

## CREATE USE INTENSITY RASTER
```{r}
createRaster = function(coef) {
  rest.raster =
    scaled.elev * coef[2] +
    scaled.slope * coef[3] +
    scaled.water * coef[4] +
    scaled.salt * coef[5] +
    scaled.herb * coef[6] +
    scaled.SHR * coef[7]
  rest.raster = exp(rest.raster)
  rest.raster = rest.raster / sum(as.data.frame(rest.raster, na.rm = T))
  return(rest.raster)
}

MasterRasterSimple = stack(apply(X = cf.all, FUN = createRaster, MARGIN = 2))
MeanAngusAll = calc(MasterRasterSimple[[c(1,2,4,6)]], fun = mean)
MeanCriolloAll = calc(MasterRasterSimple[[c(3,5,7,8,9)]], fun = mean)
MasterRasterSimple = addLayer(MasterRasterSimple, c(MeanAngusAll, MeanCriolloAll))
names(MasterRasterSimple) = c(indivBreed, 'Angus', 'Criollo')
plot((MasterRasterSimple[[10:11]]))
MasterFrameAll = as.data.frame(MasterRasterSimple, xy = T) %>%
  pivot_longer(cols = 3:13)
names(MasterFrameAll) = c('x', 'y', 'BREED', 'value')

ggplot() +
  geom_raster(data = subset(MasterFrameAll, BREED == 'Angus' |
                              BREED == 'Criollo'),
              aes(x = x, y = y, fill = value)) +
  scale_fill_viridis_c(na.value = 'white', option = 'turbo', direction = 1,
                       trans = 'log') +
  geom_point(data = DPcattle.track.cropped, aes(x = x_, y = y_),
             alpha = 0.2, size = 0.1) +
  # geom_sf(data = roads, color = 'white') +
  coord_sf(datum = sf::st_crs(drill_pasture)) +
  facet_wrap(~BREED) + 
  scale_x_continuous(breaks = seq(621000, 624000, length.out = 2)) +
  scale_y_continuous(breaks = seq(4221000, 4225000, length.out = 3)) +
  theme(text = element_text(color = "black", size = 20),
        legend.key.size = unit(1.5, 'cm')) +
  labs(title = 'Mean Relative Use Intensity', fill = 'Log(Intensity)')

# ggsave('log relative use.png', plot = last_plot(),
#   width = 10, height = 7, units = 'in', dpi = 300, limitsize = TRUE)
# 
# k =  projectRaster(log(MasterRasterSimple[[10]]),
#                    crs="+proj=longlat +datum=WGS84", method='ngb')
# KML(k, filename = 'Angus', overwrite = T)
# l =  projectRaster(log(MasterRasterSimple[[11]]),
#                    crs="+proj=longlat +datum=WGS84", method='ngb')
# KML(l, filename = 'Criollo', overwrite = T)

```

## Make a map for Eric
```{r}
ggplot() +
  geom_raster(data = subset(MasterFrameAll, BREED == 'Angus' | 
                              BREED == 'Criollo'),
              aes(x = x, y = y, fill = value)) +
  scale_fill_viridis_c(na.value = 'white', option = 'turbo', direction = 1,
                       trans = 'log') +
  geom_sf(data = features[1:10,], aes(shape = Description), alpha = 0.8) +
  coord_sf(datum = sf::st_crs(drill_pasture)) +
  facet_wrap(~BREED) + 
  scale_x_continuous(breaks = seq(621000, 624000, length.out = 2)) +
  scale_y_continuous(breaks = seq(4221000, 4225000, length.out = 3)) +
  theme(text = element_text(color = "black", size = 20),
        legend.key.size = unit(1.5, 'cm'),
        panel.background = element_rect(fill = "transparent"),
        plot.background = element_rect(fill = "transparent", color = NA), 
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  labs(title = 'Mean Relative Use Intensity', shape = 'Feature Type', 
       fill = 'Log(Intensity)')

ggsave('Angus Rel Use with Features.png', plot = last_plot(),
  width = 12, height = 7, units = 'in', dpi = 300, limitsize = TRUE)
```

