---
title: "full year heat map 2022"
author: "Maria Stahl"
date: "1/19/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
rm(list = ls())
```

### load packages
```{r}
library(dplyr)
library(ggplot2)
library(htmlwidgets)
library(leaflet)
library(lubridate)
library(rgdal)
library(sf)
```


## Load in pasture shapefiles
```{r}
cottonwood = read_sf("./../../spatial data/Cottonwood_Allotment_and_pasture_boundaries/Cottonwood_Allotment_and_pasture_boundaries.shp")

indianCreek = read_sf("./../../spatial data/Cottonwood_Allotment_and_pasture_boundaries/BLM_IndianCreekAllotment.shp")

winterUSU = read_sf("./../../spatial data/USU_study_winter_pastures_dissolve/USU_study_winter_pastures_dissolve.shp")
```

### Read in collar data, reproject to UTM, and convert to sf object
```{r}
# read in data
cattle.dat = read.csv('../processed data/2021-2022_GPS-combined.csv')

# convert to sf object
cattle.gps = st_as_sf(cattle.dat, coords = c('Longitude', 'Latitude'))
st_crs(cattle.gps) = CRS("+proj=longlat +ellps=WGS84")

# reproject to UTM
cattle.gps$geometry = st_transform(cattle.gps$geometry, 
                         crs = st_crs(cottonwood))

st_crs(cattle.gps) == st_crs(indianCreek)

# convert dates to posixct
cattle.gps$date_time = as.POSIXct(cattle.gps$date_time)

# convert breed to factor
cattle.gps$breed = as.factor(cattle.gps$breed)
```

### plot all points on top of pastures
```{r}
# ggplot() +
#   geom_sf(data = cottonwood) +
#   geom_sf(data = indianCreek) +
#   geom_sf(data = cattle.gps, alpha = 0.5)

```

### merge sf objects
```{r}
cwood = cottonwood %>%
  dplyr::select(PASTURE_NA, geometry)
names(cwood) = c('Pasture', 'geometry')

icreek = indianCreek %>%
  dplyr::select(Pasture, geometry)

USU = winterUSU %>%
  dplyr::select(USU_pastur, geometry) %>%
  rename(Pasture = USU_pastur)

pastures = rbind(cwood, USU)
```

### remove points outside of pasture boundaries
```{r}
points.in = st_intersection(pastures, cattle.gps, sparse = F)
```

### make smaller cattle points data.frame for faster plotting
```{r}
# select every 100th point from points.in
points.in.small = points.in[seq(1, nrow(points.in), 100),]
```

### plot small points df on top of pastures
```{r}

# # add column for 'month' in points.in.small
# points.in.small = points.in.small %>% 
#   mutate(month = month(date_time))
# 
# ggplot() +
#   geom_sf(data = pastures, fill = 'white', linewidth = 1.25) +
#   # geom_sf(data = subset(points.in.small),
#   #         aes(color = as.factor(month)), alpha = 0.5) +
#   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
#         panel.background = element_blank(), 
#         axis.line = element_line(colour = "black"))

```

### create color-coded map of pastures
```{r}
### add column for season in pastures sf
pastures = pastures %>%
  mutate(season = case_when(Pasture == 'Park Pasture' ~  'Jan-Feb',
                            Pasture == 'Creek Pasture' ~  'Mar',
                            Pasture == 'Drill Pasture' ~  'Apr',
                            Pasture == 'Davis' ~  'May',
                            Pasture == 'Lavender' ~  'May',
                            Pasture == 'Corral Pocket' ~ 'Nov-Dec',
                            T ~ 'Jun-Oct')) %>%
  mutate(season = ordered(season,
                             levels = c('Jan-Feb', 'Mar', 'Apr', 'May', 
                                        'Jun-Oct', 'Nov-Dec')))

### add shorthand pasture names
pastures = pastures %>%
  mutate(short.name = case_when(Pasture == 'Park Pasture' ~  'Park',
                            Pasture == 'Creek Pasture' ~  'Creek',
                            Pasture == 'Drill Pasture' ~  'Drill',
                            Pasture == 'Davis' ~  'Davis',
                            Pasture == 'Lavender' ~  'Lavender',
                            Pasture == 'Corral Pocket' ~ 'Corral Pocket',
                            T ~ 'NA')) %>%
  mutate(short.name = ordered(short.name,
                             levels = c('Park', 'Creek', 'Drill', 'Davis', 
                                        'Lavender', 'NA', 
                                        'Corral Pocket')))
### create data.frame with centroids
pastures = pastures %>%
  cbind(., st_coordinates(st_centroid(pastures)))

### create color palette for fill colors
colors = c('#99ddff', '#44bb99', '#bbcc33', '#aaaa00', '#eedd88', '#ee8866')

### make map
ggplot() + 
  geom_sf(data = pastures, aes(fill = season)) +
  geom_label(data = subset(pastures, short.name != 'NA'), 
                           aes(x = X, y = Y, label = short.name), size = 3.5) +
  scale_fill_manual(values = colors)

# ggsave('../figures/yearly rotation.png', plot = last_plot(), scale = 1)
```

### look at each pasture separately for spatial partitioning
## PARK
```{r}
# isolate pasture
park = subset(pastures, Pasture == 'Park Pasture')

# isolate points over pasture and transform to lat long
park.points = st_intersection(park, cattle.gps, sparse = F) %>%
  st_transform(CRS("+proj=longlat +datum=WGS84"))

# transform park pasture
park = park %>% st_transform(CRS("+proj=longlat +datum=WGS84"))

# plot points over pasture
# ggplot() +
#   geom_sf(data = park, fill = 'white', linewidth = 1.25) +
#   geom_sf(data = park.points,
#           aes(color = breed), alpha = 0.5) +
#   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
#         panel.background = element_blank(),
#         axis.line = element_line(colour = "black"))

factpal = colorFactor(c('#6c071c', '#00447c'), park.points$breed)

park.map = leaflet() %>% 
  addPolygons(data = park, fill = NA, color = 'white') %>%
  addCircleMarkers(data = park.points, radius = .25,
                   color = ~factpal(breed), opacity = .25) %>%
  addLegend(data = park.points, position = "topright", pal = factpal, values = ~breed,
            opacity = 1) %>%
  addProviderTiles("Esri.WorldImagery")

park.map

saveWidget(park.map, '../figures/2021-2022 leaflet maps/parkMap.html', 
           selfcontained = FALSE)

```

## CREEK
```{r}
# isolate pasture
creek = subset(pastures, Pasture == 'Creek Pasture')

# isolate points over pasture and transform to lat long
creek.points = st_intersection(creek, cattle.gps, sparse = F) %>%
  st_transform(CRS("+proj=longlat +datum=WGS84"))

# transform park pasture
creek = creek %>% st_transform(CRS("+proj=longlat +datum=WGS84"))

creek.map = leaflet() %>% 
  addPolygons(data = creek, fill = NA, color = 'white') %>%
  addCircleMarkers(data = creek.points, radius = .25,
                   color = ~factpal(breed), opacity = .25) %>%
  addLegend(data = creek.points, position = "topright", pal = factpal, 
            values = ~breed, opacity = 1) %>%
  addProviderTiles("Esri.WorldImagery")

park.map

saveWidget(creek.map, '../figures/2021-2022 leaflet maps/creekMap.html', 
           selfcontained = FALSE)

```

## DRILL
```{r}
# isolate pasture
drill = subset(pastures, Pasture == 'Drill Pasture')

# isolate points over pasture and transform to lat long
drill.points = st_intersection(drill, cattle.gps, sparse = F) %>%
  st_transform(CRS("+proj=longlat +datum=WGS84"))

# transform park pasture
drill = drill %>% st_transform(CRS("+proj=longlat +datum=WGS84"))

drill.map = leaflet() %>% 
  addPolygons(data = drill, fill = NA, color = 'white') %>%
  addCircleMarkers(data = drill.points, radius = .25,
                   color = ~factpal(breed), opacity = .25) %>%
  addLegend(data = drill.points, position = "topright", pal = factpal, 
            values = ~breed, opacity = 1) %>%
  addProviderTiles("Esri.WorldImagery")

saveWidget(drill.map, '../figures/2021-2022 leaflet maps/drillMap.html', 
           selfcontained = FALSE)

```

## DAVIS AND LAVENDER
```{r}
# isolate pasture
davis.lav = subset(pastures, Pasture == 'Davis' |
                     Pasture == 'Lavender')

# isolate points over pasture and transform to lat long
davis.lav.points = st_intersection(davis.lav, cattle.gps, sparse = F) %>%
  st_transform(CRS("+proj=longlat +datum=WGS84"))

# transform park pasture
davis.lav = davis.lav %>% st_transform(CRS("+proj=longlat +datum=WGS84"))

davis.lav.map = leaflet() %>% 
  addPolygons(data = davis.lav, fill = NA, color = 'white') %>%
  addCircleMarkers(data = davis.lav.points, radius = .25,
                   color = ~factpal(breed), opacity = .25) %>%
  addLegend(data = davis.lav.points, position = "topright", pal = factpal, 
            values = ~breed, opacity = 1) %>%
  addProviderTiles("Esri.WorldImagery")

saveWidget(davis.lav.map, '../figures/2021-2022 leaflet maps/davisLavMap.html', 
           selfcontained = FALSE)

```

## CORRAL POCKET
```{r}
# isolate pasture
corral = subset(pastures, Pasture == 'Corral Pocket')

# isolate points over pasture and transform to lat long
corral.points = st_intersection(corral, cattle.gps, sparse = F) %>%
  st_transform(CRS("+proj=longlat +datum=WGS84"))

# transform park pasture
corral = corral %>% st_transform(CRS("+proj=longlat +datum=WGS84"))

factpal = colorFactor(c('#6c071c', '#00447c'), corral.points$breed)

corral.map = leaflet() %>% 
  addPolygons(data = corral, fill = NA, color = 'white') %>%
  addCircleMarkers(data = corral.points, radius = .25,
                   color = ~factpal(breed), opacity = .25) %>%
  addLegend(data = corral.points, position = "topright", pal = factpal, 
            values = ~breed, opacity = 1) %>%
  addProviderTiles("Esri.WorldImagery")

saveWidget(corral.map, '../figures/2021-2022 leaflet maps/corralMap.html', 
           selfcontained = FALSE)

```

## PNG of all sites
```{r}

webshot('../figures/2021-2022 leaflet maps/parkMap.html', 
        file = '../figures/2021-2022 leaflet maps/parkMap.png',
        cliprect = "viewport")

webshot('../figures/2021-2022 leaflet maps/creekMap.html', 
        file = '../figures/2021-2022 leaflet maps/creekMap.png',
        cliprect = "viewport")

webshot('../figures/2021-2022 leaflet maps/drillMap.html', 
        file = '../figures/2021-2022 leaflet maps/drillMap.png',
        cliprect = "viewport")

webshot('../figures/2021-2022 leaflet maps/davisLavMap.html', 
        file = '../figures/2021-2022 leaflet maps/davisLavMap.png',
        cliprect = "viewport")

webshot('../figures/2021-2022 leaflet maps/corralMap.html', 
        file = '../figures/2021-2022 leaflet maps/corralMap.png',
        cliprect = "viewport")



```